\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-09-25 paper.qmd
Added animation links for Figure 15

```{r}
#| echo: false
#| fig-cap: "Model in \\gD{}, on the layout a and b, and two views of the fit in projections from $9\\text{-}D$, for the PBMC3k data ($n =  2622$ and $p = 9$). Layout a shows three-well separated clusters with big separation, while layout b shows close clusters. In $9\\text{-}D$, the data shows three clusters with two of them close and one is separated from others. This is why b1, b2, and b3 shows a connected edge between the close clusters, as proven by @fig-pbmc-mse as a best layout. Viewing the fitted model in $9\\text{-}D$, helps to see some unobserved patterns of the data: (i) dense points, and (ii) non-linear clusters. Videos of the langevitour animations for the models are available at <https://youtu.be/0cKX_HG_n0k> and <link2> respectively."
#| label: fig-model-pbmc-author-proj
#| fig-pos: H
#| fig-width: 10
#| fig-height: 15
#| out-height: 80%

>>>>

```{r}
#| echo: false
#| fig-cap: "Model in \\gD{}, on the layout a and b, and two views of the fit in projections from $9\\text{-}D$, for the PBMC3k data ($n =  2622$ and $p = 9$). Layout a shows three-well separated clusters with big separation, while layout b shows close clusters. In $9\\text{-}D$, the data shows three clusters with two of them being close and one separated from the others. This is why b1, b2, and b3 shows a connected edge between the close clusters, as proven by @fig-pbmc-mse as a best layout. Viewing the fitted model in $9\\text{-}D$, helps to see some unobserved patterns of the data: (i) dense points, and (ii) non-linear clusters. Videos of the langevitour animations for the models are available at <https://youtu.be/0cKX_HG_n0k> and <https://youtu.be/KhJvsRtaX04> respectively."
#| label: fig-model-pbmc-author-proj
#| fig-pos: H
#| fig-width: 10
#| fig-height: 15
#| out-height: 80%

### 2024-09-25 paper.tex
Added animation links for Figure 15

\caption{\label{fig-model-pbmc-author-proj}Model in \gD{}, on the layout
a and b, and two views of the fit in projections from \(9\text{-}D\),
for the PBMC3k data (\(n =  2622\) and \(p = 9\)). Layout a shows
three-well separated clusters with big separation, while layout b shows
close clusters. In \(9\text{-}D\), the data shows three clusters with
two of them close and one is separated from others. This is why b1, b2,
and b3 shows a connected edge between the close clusters, as proven by
Figure~\ref{fig-pbmc-mse} as a best layout. Viewing the fitted model in
\(9\text{-}D\), helps to see some unobserved patterns of the data: (i)
dense points, and (ii) non-linear clusters. Videos of the langevitour
animations for the models are available at
\url{https://youtu.be/0cKX_HG_n0k} and respectively.}

>>>>

\caption{\label{fig-model-pbmc-author-proj}Model in \gD{}, on the layout
a and b, and two views of the fit in projections from \(9\text{-}D\),
for the PBMC3k data (\(n =  2622\) and \(p = 9\)). Layout a shows
three-well separated clusters with big separation, while layout b shows
close clusters. In \(9\text{-}D\), the data shows three clusters with
two of them being close and one separated from the others. This is why
b1, b2, and b3 shows a connected edge between the close clusters, as
proven by Figure~\ref{fig-pbmc-mse} as a best layout. Viewing the fitted
model in \(9\text{-}D\), helps to see some unobserved patterns of the
data: (i) dense points, and (ii) non-linear clusters. Videos of the
langevitour animations for the models are available at
\url{https://youtu.be/0cKX_HG_n0k} and
\url{https://youtu.be/KhJvsRtaX04} respectively.}
